Why robot programming is hard

### 2014-08-18 paper.tex
More references

\title {Why robot programming is hard}
\author {Tessa Lau \\
Savioke Inc.\\
Buenos Aires, Argentina \\
{\tt tlau@tlau.org}
}
\maketitle

@@

All these innovations have become possible through multiple advances: in sensor technology, which robots use to perceive the world around them; in planning and navigation, which enable robots to move around in the world unaided; in human-safe motion controllers, which let robots move their limbs without endangering the people around them; in the ROS open source robot operating system, which enables roboticists to build on each others' work without starting from scratch; and many more advances in the broader field of robotics.

>>>>

\title {Why robot programming is hard}
\author {Tessa Lau \\
Savioke Inc.\\
Santa Clara, CA\\
{\tt tlau@savioke.com}
}
\maketitle

@@

All these innovations have become possible through multiple advances: in sensor technology, which robots use to perceive the world around them~\cite{henry-iser10}; in planning and navigation, which enable robots to move around in the world unaided~\cite{jackel-cacm07}; in human-safe motion controllers, which let robots move their limbs without endangering the people around them~\cite{kemp-ieee07}; in the ROS open source robot operating system, which enables roboticists to build on each others' work without starting from scratch~\cite{quigley-icra09}; and many more advances in the broader field of robotics.
